Behavior Driven Development in Haskell

### 2012-05-24 paper.tex
writing problems.

\noindent Our {\tt doctest} implementation 
can be used for design, documentation and automatic testing.
We hope that this kill-three-birds-with-one-stone aspect 
motives Haskellers to write test code.

@@

BDD tools used in other programming language communities are
mainly based on example test. When we bring them to
Haskell community, we should integrate them with properties test.

We can categorize behaviors into two types: visible behaviors
and internal behaviors.
Visible behaviors are those which are useful for for both developers and users.
By contrast, internal behaviors are those which are usefull only for developers.
Behavior for a corner case registered in a bug track system is
a good example of internal behaviors.

BDD tools should be treat both of them and provide functionality
to disclose visible behaviors as documentation for users.

TBD: doctest and comments

@@

Haddock version 2.7.2 or earlier does not provide annotation syntax 
for examples and properties.

@@

>>>>

\noindent Our {\tt doctest} implementation 
can be used for design, documentation and automatic testing.
We hope that this kill-three-birds-with-one-stone aspect 
motivates Haskellers to write test code.

@@

BDD tools used in other programming language communities are
mainly based on example test
and do not support property test.
To our experience, it is not difficult to find properties for 
pure Haskell functions.
So, when we bring BDD tools to
Haskell community, we should integrate them with properties test.

We can categorize behaviors into two types: visible behaviors
and internal behaviors.
Visible behaviors are those which are useful for both developers and users.
By contrast, internal behaviors are those which are usefull only for developers.
Behavior for a corner case registered in a bug track system is
a good example of internal behaviors.

BDD tools should be treat both of them and provide functionality
to disclose visible behaviors as documentation for users.
If we can archive this, BDD tools can be used for
triple purpose: design, documentation and automatic testing.

A good candidate for this is {\tt doctest} in Python community.
It extends Python's documentation strings so that they
can contain examples. 
Examples can be tested by the Python interpreter.

@@

@@

TBD: Haddock version 2.7.2 or earlier does not provide annotation syntax 
for examples and properties.
